---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.path = "man/figures/README-",
  fig.align = "center",
  out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

# rucoin

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/bagasbgy/rucoin.svg?branch=master)](https://travis-ci.org/bagasbgy/rucoin)
<!-- badges: end -->

## Installation

You can install the development version of `rucoin` using:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("bagasbgy/rucoin")
```

## Getting Started

First of all, let's start by importing the library:

```{r}
# import library
library(rucoin)
```

### API Authorization

Some function in this package requires private access and need a proper API key, secret, and passphrase. If you don't have any, or need more information, please visit the [Generating an API Key](https://docs.kucoin.com/#generating-an-api-key){target="_blank} section in the official API documentation.

Current functions that need API authorization are:

* `post_kucoin_market_order()`
* `get_kucoin_balances()`
* `get_kucoin_order()`

#### Setting-up API Key

To setup the API, the recommended way is using `.Renviron` file, which could be conveniently done using [`usethis::edit_r_environ()`](https://usethis.r-lib.org/reference/edit.html){target="_blank"}:

```{r, eval=FALSE}
# you can also use `scope = "project"` for local environment
usethis::edit_r_environ(scope = "user")
```

In the `.Renviron` file, insert your API key details as follow:

```
KC-API-KEY = XXXXXXXXXX
KC-API-SECRET = XXXXXXXXXX
KC-API-PASSPHRASE = XXXXXXXXXX
```

### Market Data

**All market data is publicly accessible, and could be accessed without API authorization.**

For getting historical data, you can use `get_kucoin_prices()`:

```{r}
# get one pair of symbol prices
prices <- get_kucoin_prices(
  symbols = "KCS/USDT",
  from = "2019-06-01 00:00:00",
  to = "2019-06-02 00:00:00",
  frequency = "1 hour"
)

# quick check
prices
```

The `get_kucoin_prices()` function also support for querying multiple symbols:

```{r}
# get one pair of symbol prices
prices <- get_kucoin_prices(
  symbols = c("KCS/USDT", "BTC/USDT", "KCS/BTC"),
  from = "2019-06-01 00:00:00",
  to = "2019-06-02 00:00:00",
  frequency = "1 hour"
)

# quick check
prices
```

You can also get the most recent metadata for all symbols using `get_kucoin_symbols()`:

```{r}
# get all symbols' most recent metadata
metadata <- get_kucoin_symbols()

# quick check
metadata
```

### Get User Information

**All user information data is private, and need API authorization.**

To get the balance information, you can use `get_kucoin_balance()`:

```{r, eval=FALSE}
# get user's balance details
balances <- get_kucoin_balances()

# quick check
balances
```

### Post an Order

**All order posting functions are private, and need API authorization.**

#### Market Order

Here is an example of posting a market order:

```{r, eval=FALSE}
# post a market order: buy 1 KCS
order_detail <- post_kucoin_market_order(
  symbol = "KCS/BTC",
  side = "buy",
  base_size = 1
)

# quick check
order_detail
```
