---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "man/figures/README-",
    fig.align = "center",
    out.width = "100%",
    collapse = TRUE,
    comment = "#>"
)

options("datatable.print.topn" = 3, "datatable.print.nrows" = 50, "datatable.print.class" = TRUE, "datatable.print.trunc.cols" = TRUE)
```

# Tutorials

Once you've installed and set up your api key you can follow this tutorial; see the [README](README.md) for these details.

## Generate deposit address

This will allow to see information as to what chains etc are available for a given currency; you can use this to then generate a deposit address.

Let's show an example of generating a deposit address for `BTC`:

```{r}
currency <- "BTC"

currency_details <- kucoin::get_currency_details(currency)

currency_details

kucoin::get_deposit_address(currency, currency_details$chain_name[1])
```

## Getting and plotting market data

Let's get some market data for `BTC`:

```{r}
# get one pair of symbol prices
dt <- kucoin::get_market_data(
    symbols = "BTC/USDT",
    from = "2022-11-05 00:00:00",
    to = "2022-11-08 00:00:00",
    frequency = "1 hour"
)

dt
```
